Active Intent Disambiguation for \\ Shared Autonomy Robots

### 2019-08-02 LatexStuff_Revision_2/Reviews (copy)/information_on_response_to_reviewers/paper_review_response_template/reviewresponse_example.tex

\section{Reviewer 1}

\rcomment{
Metrics using only the number of mode switches are not sufficient for the research in robot-assisted human daily activity field. With the goal to improve task performance, the metric directly quantifying task performance will be needed. In addition, how human users perceive the presented methods are missing, which is essential for human-centered assistance. Without these two evaluation aspects, the effectiveness of the systems can probably not be demonstrated. 
}

\textbf{Response}

\subsection{User Survey}
As a part of our experiment we had conducted subjective evaluation of the algorithm by administering a survey questionnaire at the end of each phase (for each task). We chose not to include the user survey results in the previous versions of the manuscript due to space constraints. We wholeheartedly agree with the reviewer's observation that user perception is an important factor for the evaluation of human-centered assistance. Therefore, we have decided to include the user survey results in this version. To that end, we had reduce the sizes of some of the images (one column instead of two columns).

@@

Overall the users rated the usefulness of the disambiguation algorithm fairly high and found that task execution was easier for disambiguating trials. This indicates that a reduction in the number of button presses has a huge positive impact on task performance

\subsection{Task Success and Task Completion Times}
As per the reviewer's suggestion we analyzed the task completion times and we are reporting the results in this revision. As our algorithm was not time optimized and also due to the lack of transparency regarding \textit{why} the autonomy is choosing the disambiguation modes, a statistically significant difference was not observed between the manual and disambiguation. However, an overall trend of a reduction in variance was observed in the the disambiguating trials indicating that the task performance was in general more consistent. We also report the overall task success (94.53$\%$).

@@

The reviewer's comment inspired us to look even more closely into the inner workings of the field-theoretic approach and conduct simulation-based quantitative evaluation of the different intent inference approaches. 
A new section has been added to discuss the advantages of field-theoretic approach in the context of assistive robotics.

A key requirement of an intent inference algorithm in the context of assistive setting is that it should be able reason about goal probabilities in the \textbf{absence} of useful information. In our system we rely solely on user control commands as our evidence variable for inference. Subjects may not issue velocity control commands for large chunks of time due to fatigue, motor impairment, mode switches, cognitive load etc.

We show that in the absence of control commands our field-theoretic approach converges according to the \textit{principle of maximum entropy} to a uniform distribution whereas recursive Bayesian approaches as implemented in [23] converges to the stationary distribution of the underlying goal transition matrix which can potentially create unwanted biases in the inference.

We have replaced the qualitative comparison with a simulation-based quantitative comparison of memory-based, recursive Bayesian and the field-theoretic approach. The inference accuracy for field-theoretic approach was comparable to the recursive Bayesian updating but significantly better than the memory-based approach indicating no degradation in inference accuracy when the control commands are available.

@@

\section{Reviewer 2}

We are glad that you were happy with the submitted version. In this revised version we have further improved different sections of the paper according to the suggestions by Reviewer 1 and we believe that this has significantly strengthened our paper.

### 2019-08-02 LatexStuff_Revision_2/bare_jrnl.tex
Revision 2 final

\documentclass[journal]{IEEEtran}
%
%\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{changes}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure}
\usepackage{mathtools, bbm}
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{lipsum}
\usepackage[export]{adjustbox}
\usepackage[normalem]{ulem} % underline
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{balance}
\usepackage{color}
\usepackage{url}
\usepackage{tablefootnote}
\usepackage{microtype}
\usepackage{algorithm, algorithmic}
\usepackage{breqn}
\usepackage[bottom]{footmisc}

@@

%We use the framework of dynamic neural fields to specify the time evolution of the probability distribution $\boldsymbol{p}(t)$, in which we treat the individual goal probabilities $p^i(t)$ as constrained dynamical state variables such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$. 
%The dynamical system can be generically written as 
%\begin{equation*}
%\dot{\boldsymbol{p}}(t) = F(\boldsymbol{p}(t), \boldsymbol{u}_h ; \boldsymbol{\Theta})
%\end{equation*}
%where $F$ represents a nonlinear vector field, $\boldsymbol{u}_h$ is the human control input and $\boldsymbol{\Theta}$ represents all other task-relevant features that affect the time-evolution of the probability distribution. 
The full specification of the field is given by
%The time evolution of the probability distribution is given by
%\begin{multline}\label{eq:dft}
%\frac{\partial \boldsymbol{p}(t)}{\partial t} = \frac{1}{\tau}\bigg[-\mathbb{I}_{n_g\times n_g}\cdot\boldsymbol{p}(t) + \underbrace{\frac{1}{n_g}\cdot\mathbbm{1}_{n_g}\bigg]}_{\text{rest state}} \\+  \underbrace{\boldsymbol{\lambda}_{n_g\times n_g}\cdot\sigma(\boldsymbol{\xi}(\boldsymbol{u}_h;\boldsymbol{\Theta}))}_{\text{excitatory + inhibitory}}
%\end{multline}
%\begin{equation}
%\begin{equation*}
%\frac{\partial \boldsymbol{p}(t)}{\partial t} = \frac{1}{\tau}\bigg[-\mathbb{I}_{n_g\times n_g}\cdot\boldsymbol{p}(t) + \underbrace{\frac{1}{n_g}\cdot\mathbbm{1}_{n_g}\bigg]}_{\text{rest state}} 
%\end{equation*}
\begin{equation*}
\frac{\partial \boldsymbol{p}(t)}{\partial t} = \frac{1}{\tau_1}\bigg[\underbrace{-\boldsymbol{P}_{n_g\times n_g}\cdot\boldsymbol{p}(t)}_{\text{goal_transition_dynamics}}\bigg] +\frac{1}{\tau_2}\bigg[\underbrace{\frac{1}{n_g}\cdot\mathbbm{1}_{n_g}}_{\text{rest state}}\bigg]
\end{equation*}
%\begin{equation*}
%\frac{\partial \boldsymbol{p}(t)}{\partial t} = \frac{1}{\tau_1}\bigg[\underbrace{-\boldsymbol{P}_{n_g\times n_g}\cdot\boldsymbol{p}(t)}_{\text{goal transition dynamics}}\bigg] + \underbrace{\frac{1}{n_g\cdot\tau_2}\cdot\mathbbm{1}_{n_g}}}}_{\text{rest state}} 
%\end{equation*}
\begin{equation}\label{eq:dft_ii}
+  \underbrace{\boldsymbol{\lambda}_{n_g\times n_g}\cdot\sigma(\boldsymbol{\xi}(\boldsymbol{u}_h;\boldsymbol{\Theta}))}_{\text{excitatory + inhibitory}}
\end{equation}
%\end{equation}

where $\boldsymbol{u}_h$ is the human control input and $\boldsymbol{\Theta}$ represents all other task-relevant features, time-scale parameters $\tau_1, \tau_2$ determine the memory capacity and decay behavior, $\boldsymbol{P}_{n_g\times n_g}$ is the state transition matrix for the embedded Markov chain that models the goal transitions as jump processes, $\mathbbm{1}_{n_g}$ is a vector of dimension $n_g$ containing all ones, $\boldsymbol{\lambda}$ is the control matrix that controls the excitatory and inhibitory aspects, $\boldsymbol{\xi}$ is a function that encodes the nonlinearity through which human control commands and task features affect the time evolution, and $\sigma$ is a biased sigmoidal nonlinearity given by $\sigma(\boldsymbol{\xi}) = \frac{1}{1 + e^{-\boldsymbol{\xi}}} - 0.5$.

@@

\subsection{\added{Field-Theoretic Intent Inference For Assistive Robotics}}\label{ssec:dft_adv}
\begin{figure}[b]
	\centering
	\includegraphics[width = 1.0\hsize]{./figures/inference_comparison_new.eps}
%	\vspace{-1cm}
	\caption{\added{Goal inference comparison: (Left to Right). Goal probabilities for Memory-Based Prediction (Left), Recursive Bayesian Belief Update (Middle) and field-theoretic inference scheme (Right) and reaching behavior in a scene with two goals. The black rectangular boxes in the plots indicates time range during which the control velocity was zeroed. The probabilities do not change much for memory-based approach as the cost function employed is purely distance-based (left). The convergence is towards the stationary and uniform distribution for recursive (middle) and field-theoretic approach (right) respectively.}}
	\label{fig:dft_inference}
\end{figure}
\added{In our work, autonomy's inference of user intent solely relies on user control commands. In the domain of assistive robotics, it is quite often the case that the user input is highly discontinuous (due to fatigue, motor impairments, stoppage for mode switches \textit{et cetera}). Therefore, it is important to reason about belief over goals in the \textit{absence} of useful information. }

\added{According to the \textit{principle of maximum entropy}, in the absence of testable information (no control commands issued by the user and uniform global prior), the belief should converge to a uniform distribution. In the absence of $\boldsymbol{u}_h$, using Equation~\ref{eq:dft_ii}, $\boldsymbol{p}(t)$ converges to a uniform distribution mimicking natural forgetting behavior and results in a more meaningful inference. The rate at which the distribution decays to a uniform distribution is controlled by $\tau_1$.}

@@

\added{
Knowledge of task-level semantics can provide informative global priors that can further improve the accuracy of the inference mechanism. Our field-theoretic approach can encode a task-level global prior in the `rest state' term. For example, in a multi-stage task such as pouring the contents of a cup into a bowl, the initial goal distribution will be biased towards the cup as it is more likely  that the user would try to reach for the cup initially. The relative values of $\tau_1$ and $\tau_2$ control the convergence behavior (whether to uniform distribution or rest state distribution respectively) in the absence of $\boldsymbol{u}_h$.}

@@

\added{In order to evaluate the performance of the field-theoretic inference approach a point robot simulation-based quantitative comparison to 1) memory-based prediction~\cite{dragan2013policy} and 2) recursive belief updating~\cite{jain2018recursive} was implemented in $\mathbb{R}^3$. The human is modeled as issuing a control command that noisily optimizes a straight-line path towards the intended goal. Signal dropout was simulated by randomly zeroing out control commands. Additionally, $\boldsymbol{u}_h$ was set to be zero for a randomly chosen section of each trial in order to compare the convergence behavior of different approaches. The number of goals varied between three and five and goal transitions were randomly sampled every five to eight time steps. 500 trials were simulated. Inference accuracy was computed as the fraction of total trial time (excluding when $\boldsymbol{u}_h = 0$) for which an algorithm correctly inferred the ground truth. Results for field-theoretic inference were comparable to recursive belief updating ($87.46\%$ and $87.43\%$ respectively) and outperformed memory-based prediction significantly ($59.15\%$). Figure~\ref{fig:dft_inference} shows an illustrative example of goal inference using the various methods. One can see that when there is no control command issued unlike the recursive belief approach, the field-theoretic approach converged to the maximum entropy uniform distribution.}

@@

\noindent{\textbf{Task Completion Times:}} 
\added{No statistical difference was observed in task completion times between the \textit{Manual} and \textit{Disambiguation} paradigm. However, the variance in the task completion times was lower in \textit{Disambiguation} paradigm (except for Joystick/SingleStep) indicating that the task performance was generally more consistent when robot control was performed in the disambiguating control modes chosen by the autonomy. Furthermore, the overall task success was $94.53\%$ (242 out of 256 trials). 10 out of the 14 unsuccessful trials happened during the multi-step task.}
\begin{figure}[h!]
	\centering
	\includegraphics[width = 1\hsize, height=0.35\vsize, ,left]{./figures/task_completion.eps}
	\caption{Task completion times between \textit{Disambiguation} and \textit{Manual} Paradigms. \textit{Left:} Grouped by control interfaces. \textit{Right:} Grouped by tasks.}
	\label{fig:task_completion}
\end{figure}

\noindent{\textbf{User Survey Results:}} 
\added{Table~\ref{table:survey_results} summarizes the results of the subject survey. Users rated the utility value of the disambiguation paradigm (\textbf{Q1}) fairly high (4.87$\pm$0.95) indicating that task execution was easier during disambiguating trials. User responses strongly validated the effectiveness of the blending-based shared control scheme (\textbf{Q3}, 6.19$\pm$0.75). The responses also showed that subjects liked to operate the robot (\textbf{Q2}) in the disambiguating modes (5.00$\pm$1.15) and overwhelming preferred (\textbf{Q6}) the \textit{Disambiguation} to the \textit{Manual} paradigm. Unsurprisingly, all users felt that it was harder to control the robot using the headarray (\textbf{Q4}) and rated the utility value of the disambiguation paradigm to be higher for robot control with the headarray (\textbf{Q5}). Only four out of the eight subjects found the \textit{Disambiguation} paradigm to be user-friendly (\textbf{Q7}) likely due to the lack of transparency in why the autonomy chose the disambiguation mode.}

\begin{table}[t]
	\centering
	\caption{Subjective Survey Results}
	%		The values in the table denote the deviation of the temporal distribution from a uniform distribution. Smaller values mean more concentrated and earlier disambiguation requests. } 
	%	\vspace{0.1cm}
	\label{table:survey_results}
	\begin{tabular}{|c|c|c|c|}
		\hline
		& Across Tasks & Single-step & Multi-step \\
		\hline
		\textbf{Q1} & 4.87 $\pm$ 0.95  & 4.88 $\pm$ 0.99 & 4.88 $\pm$ 0.99 \\
		\hline
		\textbf{Q2} & 5.00 $\pm 1.15 $ & 5.25 $\pm$ 1.28 & 4.75 $\pm$ 1.03 \\
		\hline
		\textbf{Q3} & 6.19 $\pm$ 0.75 & 6.25 $\pm$ 0.89 & 6.13 $\pm$ 0.64 \\
		\hline
		\textbf{Q4} & Head Array  & Head Array  & Head Array  \\
		\hline
		\textbf{Q5} & Head Array  & Head Array  & Head Array  \\
		\hline
		\textbf{Q6} & Disambiguation & Disambiguation & Disambiguation \\
		\hline
		\textbf{Q7} & Disamb/Manual & Disamb/Manual & Disamb/Manual\\

		\hline
	\end{tabular}
\end{table}
%\noindent{\textbf{Onset of Robot Assistance:}} One of the motivations for developing the disambiguation system was that more accurate intent inference (as a result of intent disambiguation) should allow the autonomy to step in earlier more during the course of task execution. However, our results did not reveal any differences between the two switching paradigms across tasks or across interfaces
%\begin{figure}[h!]
%	\centering
%	\includegraphics[width = 1\hsize ,center]{./figures/Fig10.eps}
%	\caption{Onset of robot assistance normalized with respect to task completion time. \textit{Left:} Across interfaces. \textit{Right:} Across tasks.}
%	\label{fig:initial_blend}
%\end{figure}
%One likely contributing factor is that disambiguation frequently was impaired by subjects choosing not to operate in the disambiguation mode after making a disambiguation request. One likely contributing factor is that disambiguation frequently was impaired by subjects choosing not to operate in the disambiguation mode after making a request. The disambiguation power of a control mode depends entirely on the observation of motion within that mode, and so in such scenarios disambiguation is effectively rendered inert.

>>>>

\documentclass[journal]{IEEEtran}
%
%\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage[final]{changes}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure}
\usepackage{mathtools, bbm}
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{lipsum}
\usepackage[export]{adjustbox}
\usepackage[normalem]{ulem} % underline
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{balance}
\usepackage{color}
\usepackage{url}
\usepackage{tablefootnote}
\usepackage{microtype}
\usepackage{algorithm, algorithmic}
\usepackage{breqn}
\usepackage[bottom]{footmisc}

@@

%We use the framework of dynamic neural fields to specify the time evolution of the probability distribution $\boldsymbol{p}(t)$, in which we treat the individual goal probabilities $p^i(t)$ as constrained dynamical state variables such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$. 
%The dynamical system can be generically written as 
%\begin{equation*}
%\dot{\boldsymbol{p}}(t) = F(\boldsymbol{p}(t), \boldsymbol{u}_h ; \boldsymbol{\Theta})
%\end{equation*}
%where $F$ represents a nonlinear vector field, $\boldsymbol{u}_h$ is the human control input and $\boldsymbol{\Theta}$ represents all other task-relevant features that affect the time-evolution of the probability distribution. 
\added{The full specification of the field is given by}
%The time evolution of the probability distribution is given by
%\begin{multline}\label{eq:dft}
%\frac{\partial \boldsymbol{p}(t)}{\partial t} = \frac{1}{\tau}\bigg[-\mathbb{I}_{n_g\times n_g}\cdot\boldsymbol{p}(t) + \underbrace{\frac{1}{n_g}\cdot\mathbbm{1}_{n_g}\bigg]}_{\text{rest state}} \\+  \underbrace{\boldsymbol{\lambda}_{n_g\times n_g}\cdot\sigma(\boldsymbol{\xi}(\boldsymbol{u}_h;\boldsymbol{\Theta}))}_{\text{excitatory + inhibitory}}
%\end{multline}
%\begin{equation}
%\begin{equation*}
%\frac{\partial \boldsymbol{p}(t)}{\partial t} = \frac{1}{\tau}\bigg[-\mathbb{I}_{n_g\times n_g}\cdot\boldsymbol{p}(t) + \underbrace{\frac{1}{n_g}\cdot\mathbbm{1}_{n_g}\bigg]}_{\text{rest state}} 
%\end{equation*}
\begin{equation*}
\frac{\partial \boldsymbol{p}(t)}{\partial t} = \frac{1}{\tau}\bigg[\underbrace{-\boldsymbol{P}^{T}_{n_g\times n_g}\cdot\boldsymbol{p}(t)}_{\text{goal_transition_dynamics}} + \underbrace{\frac{1}{n_g}\cdot\mathbbm{1}_{n_g}}_{\text{rest state}}\bigg]
\end{equation*}
%\begin{equation*}
%\frac{\partial \boldsymbol{p}(t)}{\partial t} = \frac{1}{\tau_1}\bigg[\underbrace{-\boldsymbol{P}_{n_g\times n_g}\cdot\boldsymbol{p}(t)}_{\text{goal transition dynamics}}\bigg] + \underbrace{\frac{1}{n_g\cdot\tau_2}\cdot\mathbbm{1}_{n_g}}}}_{\text{rest state}} 
%\end{equation*}
\begin{equation}\label{eq:dft_ii}
+  \underbrace{\boldsymbol{\lambda}_{n_g\times n_g}\cdot\sigma(\boldsymbol{\xi}(\boldsymbol{u}_h;\boldsymbol{\Theta}))}_{\text{excitatory + inhibitory}}
\end{equation}
%\end{equation}

\added{where $\boldsymbol{u}_h$ is the human control input and $\boldsymbol{\Theta}$ represents all other task-relevant features, time-scale parameter $\tau$ determines the memory capacity and decay behavior, $\boldsymbol{P}_{n_g\times n_g}$ is the state transition matrix for the embedded Markov chain that models the goal transitions as jump processes}, $\mathbbm{1}_{n_g}$ is a vector of dimension $n_g$ containing all ones, $\boldsymbol{\lambda}$ is the control matrix that controls the excitatory and inhibitory aspects, $\boldsymbol{\xi}$ is a function that encodes the nonlinearity through which human control commands and task features affect the time evolution, and $\sigma$ is a biased sigmoidal nonlinearity given by $\sigma(\boldsymbol{\xi}) = \frac{1}{1 + e^{-\boldsymbol{\xi}}} - 0.5$.

@@

\subsection{\added{Field-Theoretic Intent Inference For Assistive Robotics}}\label{ssec:dft_adv}
\begin{figure}[b]
	\centering
	\includegraphics[width = 1.0\hsize]{./figures/inference_comparison_new.eps}
%	\vspace{-1cm}
	\caption{\added{Goal inference comparison: (Left to Right). Goal probabilities for Memory-Based Prediction (Left), Recursive Bayesian Belief Update (Middle) and field-theoretic inference scheme (Right) and reaching behavior in a scene with two goals. The black rectangular boxes in the plots indicates time range during which the control velocity was zeroed. The probabilities do not change much for memory-based approach as the cost function employed is purely distance-based (left). The convergence is towards the stationary distribution of the goal transition matrix $\boldsymbol{P}$ and uniform distribution for recursive belief update (middle) and field-theoretic approaches (right) respectively.}}
	\label{fig:dft_inference}
\end{figure}
\added{In our work, autonomy's inference of user intent solely relies on user control commands. In the domain of assistive robotics, it is quite often the case that the user input is highly discontinuous (due to fatigue, motor impairments, stoppage for mode switches \textit{et cetera}). Therefore, it is important to reason about belief over goals in the \textit{absence} of useful information. }

\added{According to the \textit{principle of maximum entropy}, in the absence of testable information (no control commands issued by the user and uniform global prior), the belief should converge to a uniform distribution. In the absence of $\boldsymbol{u}_h$, using Equation~\ref{eq:dft_ii} and appropriately chosen time-scale parameter $\tau$, $\boldsymbol{p}(t)$ converges to a uniform distribution mimicking natural forgetting behavior and results in more meaningful inference. The rate at which the distribution decays to a uniform distribution is controlled by $\tau$.}

@@

\added{
Knowledge of task-level semantics can provide informative global priors that can further improve the accuracy of the inference mechanism. Our field-theoretic approach can encode a task-level global prior in the `rest state' term. For example, in a multi-stage task such as pouring the contents of a cup into a bowl, the initial goal distribution will be biased towards the cup as it is more likely  that the user would try to reach for the cup initially. }
%The relative values of $\tau_1$ and $\tau_2$ control the convergence behavior (whether to uniform distribution or rest state distribution respectively) in the absence of $\boldsymbol{u}_h$.}

@@

\added{In order to evaluate the performance of the field-theoretic inference approach a point robot simulation-based quantitative comparison to 1) memory-based prediction~\cite{dragan2013policy} and 2) recursive belief updating~\cite{jain2018recursive} was implemented in $\mathbb{R}^3$. The human is modeled as issuing a control command that noisily optimizes a straight-line path towards the intended goal. Signal dropout was simulated by randomly zeroing out control commands and $\tau$ was set to be 10. Additionally, $\boldsymbol{u}_h$ was set to be zero for a randomly chosen section of each trial in order to compare the convergence behavior of different approaches. The number of goals varied between three and five. Goal transitions were randomly sampled every five to eight time steps. 500 trials were simulated. Inference accuracy was computed as the fraction of total trial time (excluding when $\boldsymbol{u}_h = 0$) for which an algorithm correctly inferred the ground truth. Results for field-theoretic inference were comparable to recursive belief updating ($87.46\%$ and $87.43\%$ respectively) and outperformed memory-based prediction significantly ($59.15\%$). Figure~\ref{fig:dft_inference} shows an illustrative example of goal inference using the various methods. One can see that when there is no control command issued unlike the recursive belief approach, the field-theoretic approach converged to the maximum entropy uniform distribution.}

@@

\noindent{\textbf{\added{Task Completion Times:}}} 
\added{No statistical difference was observed in task completion times between the \textit{Manual} and \textit{Disambiguation} paradigms (Figure~\ref{fig:task_completion}). However, the variance in the task completion times was lower in \textit{Disambiguation} paradigm (except for joystick/single-step condition) indicating that the task performance was generally more consistent when robot control was performed in the disambiguating control modes chosen by the autonomy. Furthermore, the overall task success was $94.53\%$ (242 out of 256 trials). 10 out of the 14 unsuccessful trials happened during the multi-step task.}
\begin{figure}[h!]
	\centering
	\includegraphics[width = 1\hsize, height=0.35\vsize, ,left]{./figures/task_completion.eps}
	\caption{\added{Task completion times between \textit{Disambiguation} and \textit{Manual} Paradigms. \textit{Left:} Grouped by control interfaces. \textit{Right:} Grouped by tasks.}}
	\label{fig:task_completion}
\end{figure}

\noindent{\textbf{\added{User Survey Results:}}} 
\added{Table~\ref{table:survey_results} summarizes the results of the subject survey. Users rated the utility value of the disambiguation paradigm (\textbf{Q1}) fairly high (4.87$\pm$0.95) indicating that task execution was easier during disambiguating trials. User responses strongly validated the effectiveness of the blending-based shared control scheme (\textbf{Q3}, 6.19$\pm$0.75). The responses also showed that subjects liked to operate the robot (\textbf{Q2}) in the disambiguating modes (5.00$\pm$1.15) and overwhelming preferred (\textbf{Q6}) the \textit{Disambiguation} to the \textit{Manual} paradigm. Unsurprisingly, all users felt that it was harder to control the robot using the headarray (\textbf{Q4}) and rated the utility value of the disambiguation paradigm to be higher for robot control with the headarray (\textbf{Q5}). Only four out of the eight subjects found the \textit{Disambiguation} paradigm to be user-friendly (\textbf{Q7}) likely due to the lack of transparency regarding why the autonomy chose the disambiguation mode.}

\begin{table}[t]
	\centering
	\caption{\added{Subjective Survey Results}}
	%		The values in the table denote the deviation of the temporal distribution from a uniform distribution. Smaller values mean more concentrated and earlier disambiguation requests. } 
	%	\vspace{0.1cm}
	\label{table:survey_results}
	\begin{tabular}{|c|c|c|c|}
		\hline
		& \added{Across Tasks} & \added{Single-step} & \added{Multi-step} \\
		\hline
		\textbf{\added{Q1}} & \added{4.87} $\pm$ \added{0.95}  & \added{4.88} $\pm$ \added{0.99} & \added{4.88} $\pm$ \added{0.99} \\
		\hline
		\textbf{\added{Q2}} & \added{5.00} $\pm$ \added{1.15} & \added{5.25} $\pm$ \added{1.28} & \added{4.75} $\pm$ \added{1.03} \\
		\hline
		\textbf{\added{Q3}} & \added{6.19} $\pm$ \added{0.75} & \added{6.25} $\pm$ \added{0.89} & \added{6.13} $\pm$ \added{0.64} \\
		\hline
		\textbf{\added{Q4}} & \added{Head Array}  & \added{Head Array}  & \added{Head Array}  \\
		\hline
		\textbf{\added{Q5}} & \added{Head Array}  & \added{Head Array}  &\added{ Head Array}  \\
		\hline
		\textbf{\added{Q6}} & \added{Disambiguation} & \added{Disambiguation} & \added{Disambiguation} \\
		\hline
		\textbf{\added{Q7}} & \added{Disamb/Manual} & \added{Disamb/Manual} & \added{Disamb/Manual}\\
		\hline
	\end{tabular}
\end{table}
%\noindent{\textbf{Onset of Robot Assistance:}} One of the motivations for developing the disambiguation system was that more accurate intent inference (as a result of intent disambiguation) should allow the autonomy to step in earlier more during the course of task execution. However, our results did not reveal any differences between the two switching paradigms across tasks or across interfaces
%\begin{figure}[h!]
%	\centering
%	\includegraphics[width = 1\hsize ,center]{./figures/Fig10.eps}
%	\caption{Onset of robot assistance normalized with respect to task completion time. \textit{Left:} Across interfaces. \textit{Right:} Across tasks.}
%	\label{fig:initial_blend}
%\end{figure}
%One likely contributing factor is that disambiguation frequently was impaired by subjects choosing not to operate in the disambiguation mode after making a disambiguation request. One likely contributing factor is that disambiguation frequently was impaired by subjects choosing not to operate in the disambiguation mode after making a request. The disambiguation power of a control mode depends entirely on the observation of motion within that mode, and so in such scenarios disambiguation is effectively rendered inert.
